|

### 2025-01-27 doc/paper.qmd
pulling data

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices  
**CQA**: Corporate Decision-Making and Quantitative Analysis  
**DV**: Dependent Variable  
**HU**: Humboldt-Universität zu Berlin  
**IDE**: Integrated Development Environment  
**IV**: Independent Variable  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**US**: United States  
**WRDS**: Wharton Research Data Services

@@

3.

@@

------

1.	The original report references the reports prepared by national competent authorities (NCAs) responsible for audit oversight as the main source of data, where the data refers to the years 2020 and 2021 and was collected in 2022 [@EC_Report_2024, p.1]. However, this replication uses data obtained from the Audit Analytics Transparency Reports database via WRDS, which provides the latest available version as of September 2024, updated quarterly [@WRDS_Audit_Analytics_Transparency_Reports]. Due to potential adjustments and updates made to the database since the original data collection period, there may be differences that could affect the results. For example, audit firms may disclose updated information in subsequent reports, which would be reflected in the later database version rather than the historical snapshot used in the original report. Furthermore, the data vendor regularly updates its databases to correct errors and add new information, which may be included in the later data but not in the 2022 snapshot.

5.	For the purpose of replicating Figure 3, I use the `report_year` variable as the primary filter to define the relevant data for year 2021. This choice is based on the fact that `report_year` represents the idealized fiscal year of the Transparency Report, based on the *Europe Transparency Reports Data Dictionary* by Wharton Research Data Services [-@Europe_Transparency_Reports_Data_Dictionary], which aligns directly with the year-based aggregation needed for Figure 3. While the `report_period_end_date` provides the exact end date of each reporting period [@Europe_Transparency_Reports_Data_Dictionary], using `report_year` allows for a consistent, annual aggregation without requiring additional alignment of various period end dates. This approach simplifies the data extraction and ensures that all entries correspond to the fiscal year 2021.
Since the report does not specify the choice of variables used from the database, this could cause differences in the results.

## Replication Steps {#sec-replication_steps1}
The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level.

The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures. For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

CRSP/COMPUSTAT MERGED database allows for concurrent database access to CRSP’s stock data and Compustat’s fundamental data.

The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis. The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].

**Step 1: Pulling the Data and Managing the Databases**  
This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

>>>>

# List of Abbreviations
\setlength{\parindent}{0em}
**BHR**: Buy-and-Hold Returns   
**CRSP**: Center for Research in Security Prices  
**CQA**: Corporate Decision-Making and Quantitative Analysis  
**DV**: Dependent Variable  
**HU**: Humboldt-Universität zu Berlin  
**IDE**: Integrated Development Environment  
**IV**: Independent Variable  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**US**: United States  
**WRDS**: Wharton Research Data Services

@@

3. Compustat includes both active and inactive firms, and the original study does not specify filtering based on firm activity. Thus, all firms meeting the sample selection criteria (i.e., four quarterly earnings announcements per year and available stock return data) are retained, regardless of their active status today.

4. For historical analysis on securities, permanent identifiers, such as `PERMNO`, `PERMCO`, and `GVKEY` are used that never change for the duration of the company’s life span regardless of the name changes and are never being reused [@gow_empirical_2025]. In this replication, variable `PERMNO` is used instead of `PERMCO` because it uniquely identifies individual securities rather than companies, ensuring that stock returns are accurately tracked at the security level. Since firms may have multiple share classes with distinct price movements, using `PERMNO` prevents aggregation issues that could arise with `PERMCO`, which groups all share classes under one identifier.

5. The replication relies on Compustat and CRSP, linked via the CRSP/Compustat Merged (CCM) database, but with different update frequencies: Compustat (daily), CRSP (annually), and CCM (annually). Timing mismatches may arise, especially for firms with restated financials, leading to slight variations in event window alignment when calculating earnings-announcement returns. Unlike the original study, this replication uses the latest WRDS version available as of January 2025, meaning database updates may cause minor differences in firm coverage or reported values.

6. Since @ball_how_2008 analyze returns, I use `RET` variable in CRSP too to simplify the process. Bid and ask prices are ignored.

@@

## Replication Steps {#sec-replication_steps1}
The analysis involves gathering and filtering stock return and earnings announcement data, linking CRSP stock data with Compustat fundamentals, and estimating the relationship between annual returns and earnings-announcement window returns. The replication process follows a structured workflow of data pull, preparation, and analysis, ensuring consistency with the original study.

**Step 1: Pulling the Data and Managing the Databases**  
Data is pulled from the `crsp_a_ccm.ccmxpf_lnkhist`, `crsp_a_stock.dsf`, `comp_na_daily_all.fundq` tables via WRDS, using Python for data processing and regression analysis and facilitating direct access to stock price and return data from CRSP alongside firm fundamentals from Compustat, enabling a seamless link between market and accounting data. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code. While WRDS provides extensive financial datasets, documentation on precise variable selection and dataset integration is limited, requiring additional validation and cross-referencing with prior research.

This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.
